KPIs and Visualisations

### 2022-07-24 Report/KPIs and Visualisations.Rmd
Copying over updated function.

##### Creating the necessary data
```{r data}
# Function to read html file
read_proff <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    select( # removing empty column
      REGNSKAPSPERIODE:all_of(start)
    ) |> # using all_of()
    mutate( # removing whitespace
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
    filter( # removing duplicate rows
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    pivot_longer( # tidying data
      all_of(end):all_of(start),
      names_to = "year"
    ) |> # using all_of()
    mutate( # changing to real NAs and turning years into numbers
      value = na_if(value, "-"),
      year = as.integer(year),
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    fill( # filling the currency column
      valutakode,
      .direction = "updown"
    ) |>
    filter( # removing dates and redundant currency
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( # removing whitespace in numbers
      value = str_replace_all(value, "\\s", ""),
      value = as.numeric(value),
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    distinct() |> # removing any remaining duplicate rows
    pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    clean_names() |> # tidying names
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> # removing headings
    rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    arrange(desc(year)) # arranging by year
}

>>>>

##### Creating the necessary data
```{r data}
## Function to read html file --------------------------------------------------
read_proff <- function(file, start, end) {
  # Specifying encoding to deal with occasional errors
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    # removing empty column, using all_of(argument)
    select( 
      REGNSKAPSPERIODE:all_of(start)
    ) |> 
    # removing white space
    mutate( 
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    # removing duplicate table sometimes created by read_html()
    filter( 
      !row_number() > 176
    ) |>
    # removing duplicate rows
    filter( 
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    # tidying data using pivot_longer() and all_of(argument)
    pivot_longer( 
      all_of(end):all_of(start),
      names_to = "year"
    ) |> 
    # creating a currency code column and turning current currency codes into
    # NAs
    mutate( 
      # changing to real NAs
      value = na_if(value, "-"),
      # turning years into numbers
      year = as.integer(year),
      # creating a currency code column and turning current currency codes into
      # NAs
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    # filling the currency column
    fill(
      valutakode,
      .direction = "updown"
    ) |>
    # removing dates and redundant currency
    filter( 
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( 
      # removing white space in numbers
      value = str_replace_all(value, "\\s", ""),
      # turning numbers into true numbers
      value = as.numeric(value),
      # removing values that are years
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    # removing any remaining duplicate rows
    distinct() |> 
    # pivoting to create 'tidy' variables
    pivot_wider( 
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    # tidying names
    clean_names() |> 
    # removing headings from the table
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> 
    # making it clear what lonn refers to
    rename( 
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    # arranging by year for practical display
    arrange(desc(year)) 
}
